Challenges in Developing Great MCQMC Software

### 2022-07-09 MCQMC_2022_ChallengesDevelopSoftware.tex
Office Computer Updates

		\item

		\item

		\item

		\item

>>>>

		\item  \alert{Complete}---contain the components or have easy access to components in other libraries to solve real, complex problems

		\item  \alert{Accessible}---tutorials, demos, discussion forums, etc.\ for (new) users; written in a language that potential users speak; provide a consistent user interface

		\item \alert{Efficient}---in terms of compute time and memory

		\item \alert{Current}---include the latest and best algorithms

		\item  \alert{Sustainable}--have a sufficient user base and developer community for updates and maintenance

		\item \alert{Scalable}--take advantage of latest computer architectures for speed and to tackle large problems
